---
title: "preliminary_scripts"
output: html_document
date: "2023-04-05"
---

#install new packages
```{r}
#install.packages("stringdist")
#install.packages("lmerTest")
#install.packages("sjPlot")
#install.packages("Hmisc")
#install.packages("psych")
#install.packages("data.table")
```


# load packages
```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(stringdist)
library(lme4)
library(lmerTest)
library(sjPlot)
library(Hmisc)
library(psych)
library(broom)
library(data.table)
```

# import data from two sources
```{r}
sona_data = read_csv("connector-ap-sona.csv")
other_data = read_csv("connector-ap.csv")
other_data = other_data %>%
  mutate(sona_id = 1) %>%
  relocate(sona_id, .before = rt)

data = rbindlist(list(sona_data, other_data))
```


#explore the data
```{r}
nrow(data)
ncol(data)
data %>%
  group_by(subject) %>%
  count()
data %>%
  group_by(clue_type) %>%
  count()
data %>%
  group_by(subject, clue_type) %>%
  count()
```

# filter and select down to analyzable data
```{r}
trials = data %>%
  filter(type_of_trial == "experiment" | is_seen == 1)
nrow(trials)
ncol(trials)
trials %>%
  group_by(subject) %>%
  count()
trials %>%
  group_by(clue_type) %>%
  count()
trials %>%
  group_by(subject, clue_type) %>%
  count()
```

# filter subjects with imperfect attention checks
```{r}
incorrect_attentions = trials %>%
  mutate(adjusted_attention = ifelse(is_seen == 1, ifelse(stringdist(tolower(response), clue, method = "lv") < 2, 1, 0), 2)) %>%
  filter(adjusted_attention == 0)
incorrect_attentions
incorrect_attentions = incorrect_attentions %>%
  group_by(subject) %>%
  count()
trials = trials %>%
  filter(!(subject %in% incorrect_attentions$subject))
```

# filter out subjects with incomplete data
```{r}
trials_by_subject = trials %>%
  group_by(subject) %>%
  count()
insufficient_trials = trials_by_subject %>%
  filter(n < 66)
trials = trials %>%
  filter(!(subject %in% insufficient_trials$subject)) %>%
  filter(type_of_trial == "experiment")
trials %>%
  group_by(subject) %>%
  count()
```

# scale pragmatics to accessibility
```{r}
trials = trials %>%
  mutate(scaled_pragmatics = 1000000*pragmatics)
```



# split accuracy into high and low
```{r}
trials = trials %>%
  mutate(accessibility_categorical = ifelse(accessibility < mean(accessibility), "Low", "High"))
```


# plot accuracy by pragmatics and accessibility
```{r}
trials %>%
  ggplot(aes(x = scaled_pragmatics, y = accuracy, group = accessibility_categorical, color = accessibility_categorical)) + 
  geom_smooth(method = "lm") + 
  theme_few()
```

# generalized linear mixed effects model
```{r}
glmer1 = glmer(data = trials, accuracy ~ scaled_pragmatics*accessibility + (1|subject) + (1|words), family = "binomial")
summary(glmer1)
car::Anova(glmer1)
```

#descriptives
```{r}
data %>%
  group_by(subject) %>%
  count()
acc_by_subject = trials %>%
  group_by(subject) %>%
  summarise(av_acc = mean(accuracy))
mean(acc_by_subject$av_acc)
sd(acc_by_subject$av_acc)
 
c = trials %>%
  rowwise() %>%
  mutate(comma_count = str_count(all_responses, ",") + 1) %>%
  select(all_responses, comma_count)
mean(c$comma_count)
```


# split into guess1 and guess2
```{r}
x = trials %>% 
  separate(response, into = c("guess1", "guess2"), sep = ",") %>%
  mutate(guess1 = gsub("[^a-zA-Z]", "", guess1)) %>%
  mutate(guess1 = tolower(guess1)) %>%
  mutate(guess2 = gsub("[^a-zA-Z]", "", guess2)) %>%
  mutate(guess2 = tolower(guess2))
  #left_join(visit_counts)
```

# get counts of each word by clue
```{r}
x_1 = x %>%
  group_by(guess1, clue) %>%
  count()
x_2 = x %>%
  group_by(guess2,clue) %>%
  count()
guessed_words = bind_rows(x_1, x_2) %>%
  mutate(word = ifelse(!(is.na(guess1)), guess1, guess2)) %>%
  group_by(word, clue) %>%
  summarise(n = sum(n))
y = trials %>%
  group_by(clue) %>%
  count()
guessed_words = guessed_words %>%
  mutate(probability = n/y$n[match(clue, y$clue)])
```


# read guess_visit_counts
```{r}
guess_accessibility = read_csv("guess_visit_counts.csv")
```

# join accessibility with word counts
```{r}
guess_acc = guess_accessibility %>%
  filter(budget == 32)
guessed_words = guessed_words %>%
  left_join(guess_accessibility)

# conduct lmer with visit_counts predicting probability, random slopes at the clue level

guessed_words %>%
  ggplot(aes(x = visit_count, y = probability, group = budget, color = budget)) +
  geom_smooth(method = "lm") + 
  theme_few()

# MuMIn::rsquaredglmm()
```



