---
title: "preliminary_scripts"
output: html_document
date: "2023-04-05"
---

#install new packages
```{r}
#install.packages("stringdist")
#install.packages("lmerTest")
#install.packages("sjPlot")
#install.packages("Hmisc")
#install.packages("psych")
#install.packages("data.table")
#install.packages("MuMIn")
```


# load packages
```{r}
library(tidyverse)
library(car)
library(readr)
library(ggplot2)
library(ggthemes)
library(stringdist)
library(lme4)
library(lmerTest)
library(sjPlot)
library(Hmisc)
library(psych)
library(broom)
library(data.table)
library(MuMIn)
```

# import data from two sources
```{r}
sona_data = read_csv("../data/behavioral/connector-ap-sona.csv", col_types = cols(question_order = col_character(), race = col_character(), ethnicity = col_character(), hand = col_character(), alert = col_character(), anything_else = col_character(), english = col_character(), first_language = col_character(), age_learned = col_character()))
other_data = read_csv("../data/behavioral/connector-ap.csv", col_types = cols(question_order = col_character(), race = col_character(), ethnicity = col_character(), hand = col_character(), alert = col_character(), anything_else = col_character(), english = col_character(), first_language = col_character(), age_learned = col_character())) %>%
  mutate(sona_id = 1) %>%
  relocate(sona_id, .before = rt) %>%
  relocate(anything_else, .before = first_language) %>%
  mutate(education = str_extract(education, "\\d+\\.?\\d*") %>% 
              as.numeric())

data = bind_rows(sona_data, other_data) %>%
  mutate(education = str_extract(education, "\\d+\\.?\\d*") %>% 
              as.numeric())
```

# filter and select down to analyzable data
```{r}
trials = data %>%
  filter(type_of_trial == "experiment")
```

# filter out subjects with incomplete data
```{r}
insufficient_trials = trials %>%
  group_by(subject) %>%
  count() %>%
  filter(n < 60)

trials = trials %>%
  filter(!(subject %in% insufficient_trials$subject))

trials_comparison = trials

trials_comparison %>%
  group_by(subject) %>%
  count()
```

# filter based on attention checks
```{r}
attn_checks = data %>%
  filter(subject %in% trials$subject) %>%
  filter(is_seen == 1) %>%
  mutate(attn_corr = ifelse(is.na(response), 0, ifelse(stringdist(tolower(response), clue, method = "lv") < 2, 1, 0)))

subject_attn = attn_checks %>%
  group_by(subject) %>%
  summarise(n_correct = sum(attn_corr))

insufficient_attentions = subject_attn %>%
  filter(n_correct < 6)

trials = trials %>%
  filter(!(subject %in% insufficient_attentions$subject))
```

# demographic data
```{r}
demo = data %>%
  filter(subject %in% trials$subject) %>%
  filter(type_of_trial == "demographics" | type_of_trial == "not_english")

# deal with age learned english
not_english = demo %>%
  filter(!is.na(first_language))

first_language = not_english %>%
  group_by(first_language) %>%
  count()

age_learned = not_english %>%
  mutate(clean_age_learned = str_extract(age_learned, "\\d+\\.?\\d*") %>% 
              as.numeric())

al_av = age_learned %>%
  filter(!is.na(clean_age_learned)) %>%
  summarise(age_learned_average = mean(clean_age_learned))
age_learned_av = al_av$age_learned_average[1]

al_sd = age_learned %>%
  filter(!is.na(clean_age_learned)) %>%
  summarise(age_learned_stdev = sd(clean_age_learned))
age_learned_sd = al_sd$age_learned_stdev[1]

over_age_4 = age_learned %>%
  filter(clean_age_learned > 4)
n_over_age_4 = nrow(over_age_4)

trials = trials %>%
  filter(!(subject %in% over_age_4$subject))

demo = demo %>%
  filter(subject %in% trials$subject)

# final number subjects
n_subjects = nrow(trials %>%
  group_by(subject) %>%
  count())

# rest of demographics
age_gen_ed = demo %>%
  filter(!is.na(age)) %>%
  filter(!str_detect(education, "[^[:digit:].]"))

age_av = mean(age_gen_ed$age)
age_sd = sd(age_gen_ed$age)

education_av = mean(as.numeric(age_gen_ed$education))
education_sd = sd(as.numeric(age_gen_ed$education))

genders = age_gen_ed %>%
  group_by(gender) %>%
  count()

race = demo %>%
  filter(!is.na(race)) %>%
  group_by(race) %>%
  count()

eth_hand_alert_eng = demo %>%
  filter(!is.na(english))

ethnicity = eth_hand_alert_eng %>%
  group_by(ethnicity) %>%
  count()

hand = eth_hand_alert_eng %>%
  group_by(hand) %>%
  count()

alert = eth_hand_alert_eng %>%
  group_by(alert) %>%
  count()

english = eth_hand_alert_eng %>%
  group_by(english) %>%
  count()

non_sona = trials %>%
  filter(sona_id == 1) %>%
  group_by(subject) %>%
  count()
nrow(non_sona)
```

#descriptives
```{r}
acc_by_subject = trials %>%
  group_by(subject) %>%
  summarise(av_acc = mean(accuracy))
accuracy_av = mean(acc_by_subject$av_acc)
accuracy_sd = sd(acc_by_subject$av_acc)

acc_by_clues = trials %>%
  group_by(clue_type) %>%
  summarise(av_acc = mean(accuracy))
 
c = trials %>%
  rowwise() %>%
  mutate(comma_count = str_count(all_responses, ",") + 1) %>%
  select(all_responses, comma_count)
n_words_av = mean(c$comma_count)
rt_av = mean(as.numeric(trials$rt))/1000
rt_sd = sd(as.numeric(trials$rt))/1000
```

# test if accuracy differs significantly by english age and attention checks
```{r}
# first we recompile english demographic data using trials_comparison

demo_comparison = data %>%
  filter(subject %in% trials_comparison$subject) %>%
  filter(type_of_trial == "demographics" | type_of_trial == "not_english")

not_english_comp = demo_comparison %>%
  filter(!is.na(first_language))

age_learned_comp = not_english_comp %>%
  mutate(clean_age_learned = str_extract(age_learned, "\\d+\\.?\\d*") %>% 
              as.numeric())

age_before_after = age_learned_comp %>%
  select(subject, clean_age_learned) %>%
  filter(!(is.na(clean_age_learned))) %>%
  mutate(bfr_aft = ifelse(clean_age_learned < 5, "before", "after"))

# then we join average accuracy by subject with the groups they are in for when they learned english and how many attention checks they passed

trials_comparison = trials_comparison %>%
  group_by(subject) %>%
  summarise(avg_acc = mean(accuracy))

trials_comparison = left_join(trials_comparison, age_before_after, by = "subject") %>%
  mutate(bfr_aft_all = ifelse(is.na(bfr_aft), "before", bfr_aft)) %>%
  select(subject, avg_acc, bfr_aft_all)

trials_comparison = left_join(trials_comparison, subject_attn, by = "subject") %>%
  filter(n_correct == 5 | n_correct == 6)

anova1 = aov(data = trials_comparison, avg_acc ~ bfr_aft_all * n_correct)
summary(anova1)

trials_comparison %>%
  ggplot(aes(x = n_correct, y = avg_acc, group = bfr_aft_all, fill = bfr_aft_all)) + 
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "num correct", y = "avg accuracy", fill = "before/after")
```

# split accuracy into high and low
```{r}
trials = trials %>%
  mutate(accessibility_categorical = ifelse(accessibility < mean(accessibility), "Low", "High"))
trials = trials %>%
  mutate(pragmatics_categorical = ifelse(pragmatics < mean(pragmatics), "Low", "High"))
```


# plot accuracy by pragmatics and accessibility
```{r}
trials %>%
  ggplot(aes(x = pragmatics, y = accuracy, group = accessibility_categorical, color = accessibility_categorical)) + 
  geom_smooth(method = "lm") + 
  theme_few()
```

# generalized linear mixed effects model
```{r}
# center/scale accessibility and pragmatics
# now 0 means mean value of A/P and scaling bring everything to z-scores
trials = trials %>%
  mutate(center_a = as.numeric(scale(accessibility, center = TRUE, scale = TRUE)),
         center_p = as.numeric(scale(pragmatics, center = TRUE, scale= TRUE)))

## partial model
# glmer1 = glmer(data = trials, accuracy ~ center_p*center_a + (center_p |subject) + (center_p |words), family = "binomial")

# trials_comparison = trials_comparison %>%
#   mutate(center_a = as.numeric(scale(accessibility, center = TRUE, scale = TRUE)),
#          center_p = as.numeric(scale(pragmatics, center = TRUE, scale= TRUE)))
# 
# ## partial model
# glmer1_comp = glmer(data = trials_comparison, accuracy ~ center_p*center_a + (center_p |subject) + (center_p |words), family = "binomial")

# summary(glmer1_comp)

# full model: THIS IS THE FINAL MODEL YOU SHOULD REPORT!
glmer1 = glmer(data = trials, accuracy ~ center_p*center_a + (center_a*center_a|subject) + (center_p*center_a|words),
               family = "binomial", control = glmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4),
                           optimizer ='bobyqa'))

fixed_effects = fixef(glmer1)
probs = exp(fixed_effects)/(1+exp(fixed_effects))

summary(glmer1)
car::Anova(glmer1)

## plot predicted plot from model

sjPlot::plot_model(glmer1, type = "int", legend.title = "Accessibility", main = "ab") + 
  xlab("Pragmatics") +
  ylab("Accuracy") + 
  theme_few() + 
  ggtitle("")
```


## two-way ANOVA (for final presentation)
```{r}
library(rstatix)
anova_data = trials %>% select(subject, words, accuracy, clue_type) %>%
  separate(clue_type, into = c("a_level", "a", "p_level", "p")) %>%
  group_by(subject, a_level, p_level) %>%
  summarise(mean_acc = mean(accuracy)) %>%
  convert_as_factor(subject, a_level, p_level) %>% ungroup()

res.aov <- anova_test(
  data = anova_data, dv = mean_acc, wid = subject,
  within = c(a_level, p_level)
  )

get_anova_table(res.aov)
```

# examine properties of the clues
```{r}
trials_by_clue = trials %>%
  group_by(clue) %>%
  summarise(prags = mean(center_p), accs = mean(center_a), accuracy = mean(accuracy))

clues_by_prag = trials_by_clue %>%
  arrange(prags)

clues_by_accu = trials_by_clue %>%
  arrange(accuracy)

clues_by_accs = trials_by_clue %>%
  arrange(accs)

hist(trials_by_clue$accs)
hist(trials_by_clue$prags)

cor.test(trials_by_clue$prags, trials_by_clue$accs)
trials_by_clue %>%
  ggplot(aes(x = prags, y = accs)) + 
  geom_point() + 
  labs(x = "Pragmatics", y = "Accessibility") +
  theme_few()

## VIOLIN PLOT
trials %>%
ggplot(aes(x=pragmatics_categorical, y=accessibility, fill = pragmatics_categorical)) + 
  geom_violin(trim=FALSE) +
  geom_boxplot(width=0.1) +
  theme_few()

```


# split into guess1 and guess2
```{r}
x = trials %>% 
  separate(response, into = c("guess1", "guess2"), sep = ",") %>%
  mutate(guess1 = gsub("[^a-zA-Z]", "", guess1)) %>%
  mutate(guess1 = tolower(guess1)) %>%
  mutate(guess2 = gsub("[^a-zA-Z]", "", guess2)) %>%
  mutate(guess2 = tolower(guess2))
  #left_join(visit_counts)
```

# get counts of each word by clue
```{r}
x_1 = x %>%
  group_by(guess1, clue) %>%
  count()
x_2 = x %>%
  group_by(guess2,clue) %>%
  count()
guessed_words = bind_rows(x_1, x_2) %>%
  mutate(word = ifelse(!(is.na(guess1)), guess1, guess2)) %>%
  group_by(word, clue) %>%
  summarise(n = sum(n))
y = trials %>%
  group_by(clue) %>%
  count()
guessed_words = guessed_words %>%
  mutate(probability = n/y$n[match(clue, y$clue)])
```


# read guess_visit_counts
```{r}
guess_accessibility = read_csv("../data/stimuli/guess_visit_counts.csv")
```

# join accessibility with word counts
```{r}
guessed_words = guessed_words %>%
  left_join(guess_accessibility)

# conduct lmer with visit_counts predicting probability, random slopes and intercepts at the word level (since visit counts are for guesses not clues)

guessed_words %>%
  ggplot(aes(x = visit_count, y = probability, group = as.factor(budget), color = as.factor(budget))) +
  geom_smooth(method = "lm") + 
  labs(x = "Accessibility", y = "Guess Probability", color = "Budget") +
  theme_few()

models_2to16 = guessed_words %>% filter(budget < 33) %>%
  group_by(budget) %>%
  do(model = lmer(data = ., probability ~ visit_count + (visit_count|word)), 
     control = lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2000000)))

MuMIn::r.squaredGLMM(models_2to16$model[[3]])

summary(models_2to16$model[[1]])
summary(models_2to16$model[[2]])
summary(models_2to16$model[[3]])
summary(models_2to16$model[[4]])
summary(models_2to16$model[[5]])
```



